Software Citation Principles

### 2016-06-24 sc-principles/software-citation-principles.tex
final italicized statement

The goals of software include the linked ideas of crediting those responsible for software and understanding the dependencies of research products on specific software.
In the Importance principle~(\ref{principle:importance}), we state that
``software should be cited on the same basis as any other research product such as a paper or a book; that is, authors should cite the appropriate set of software products just as they cite the appropriate set of papers.''
In the case of one code that is derived from another code, citing the derived software may appear to not credit those responsible for the original software, nor recognize its role in the work that used the derived software.
However, this is really analogous to how any research builds on other research, where each research product just cites those products that it directly builds on, not those that it indirectly builds on.
Understanding these chains of knowledge and credit have been part of the history of science field for some time, though more recent work is suggesting more nuanced evaluation of the credit chains~\cite{casrai-credit, transitive_credit_json-ld}.

@@

Note that the ``unique'' in a UID means that it points to a unique, specific software. However, multiple UIDs might point to the same software.
This is not recommended, but is possible.
We strongly recommend that if there is already a UID for a version of software, no additional UID should be created.
Multiple UIDs can lead to split credit, which goes against the Credit and Attribution principle (\ref{principle:credit}).

>>>>

The goals of software citation include the linked ideas of crediting those responsible for software and understanding the dependencies of research products on specific software.
In the Importance principle~(\ref{principle:importance}), we state that
``software should be cited on the same basis as any other research product such as a paper or a book; that is, authors should cite the appropriate set of software products just as they cite the appropriate set of papers.''
In the case of one code that is derived from another code, citing the derived software may appear to not credit those responsible for the original software, nor recognize its role in the work that used the derived software.
However, this is really analogous to how any research builds on other research, where each research product just cites those products that it directly builds on, not those that it indirectly builds on.
Understanding these chains of knowledge and credit have been part of the history of science field for some time, though more recent work is suggesting more nuanced evaluation of the credit chains~\cite{casrai-credit, transitive_credit_json-ld}.

@@

Note that the ``unique'' in a UID means that it points to a unique, specific software. However, multiple UIDs might point to the same software.
This is not recommended, but is possible.
\textit{We strongly recommend that if there is already a UID for a version of software, no additional UID should be created.}
Multiple UIDs can lead to split credit, which goes against the Credit and Attribution principle (\ref{principle:credit}).
